### 2016-08-05 paper.tex
About to refactor

\begin{align}
p(s) &= p = p_0 + su \label{eqn:p} \\
q(t) &= q = q_0 + tv \label{eqn:q}
%a(s) = a = |p^x-q^x| = |p^y-q^y| \label{eqn:a}
\end{align}
For the case that the bisecting line has slope $0 \le m \le 1$, we wish to find $a = q^x-p^x$, which results in a box that touches both lines. Given a point $p$, we find $q$ by substituting in equations \eqref{eqn:p} and \eqref{eqn:q} and solving for $t$,
\begin{equation}
\label{eqn:abc}
t = \frac{p^x+p^y-(q_0^x+q_0^y)}{v^x+v^y}
\end{equation}
Thus,
\begin{align} 
a(s) &= q^x(t) - p^x(s) \nonumber \\
   &= q_0^x + v^x\frac{p^x(s)+p^y(s)-(q_0^x+q_0^y)}{v^x+v^y} - p^x(s) \nonumber \\
%   &= \frac{q_0^xv^y-q_0^yv^x+p^yv^x-p^xv^y}{v^x+v^y} \nonumber \\
   &= \frac{q_0^xv^y-q_0^yv^x+p^y(s)v^x-p^x(s)v^y}{v^x+v^y} \nonumber \\
   &= \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y+s(u^yv^x-u^xv^y)}{v^x+v^y} \nonumber \\
   &= s\frac{u^yv^x-u^xv^y}{v^x+v^y}+\frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{v^x+v^y} \label{eqn:a}
\end{align}

>>>>

To resolve conflict cells we consider pairs of lines of differing labels that intersect a cell $c$. Figure \ref{fig:conflict-resolution-x} shows two lines

\begin{align}
q(t) &= q = q_0 + tv \label{eqn:q} \\
r(f) &= r = r_0 + fw \label{eqn:r}
\end{align}
along with their bisector
\begin{align}
p(s) &= p = p_0 + su \label{eqn:p}
\end{align}
Our strategy will be to sample points $P$ on $p(u)$ (figure \ref{fig:conflict-resolution-octree}) such that an octree built on $V \cup P$ will completely ``separate'' $q$ and $r$, i.e., no descendent cell of $c$ will intersect both $q$ and $r$. We do this by ensuring that $P$ is sampled such that every box that intersects both $q$ and $r$ also intersects at least two points in $P$. Because Karras' algorithm guarantees that every leaf cell intersects at most one point, we know that no leaf cell will intersect $q$ and $r$ and thus no leaf cell will be a conflict cell.

We consider only bisecting lines with slope $0 \le m \le 1$. All other cases can be transformed to this case. We begin by fitting the smallest box centered at ??? that intersects both $q$ and $r$.

\subsubsection{Case $w^y>0$}

We wish to find $a = q^x-p^x$, which results in a box that touches both lines. Given a point $p$, we find $q$ by substituting in equations \eqref{eqn:q} and \eqref{eqn:r} and solving for $t$,
\begin{equation}
t = \frac{p^x+p^y-(q_0^x+q_0^y)}{v^x+v^y}
\end{equation}
Thus,
\begin{align} 
a(s) &= q^x(t) - p^x(s) \nonumber \\
   &= q_0^x + v^x\frac{p^x(s)+p^y(s)-(q_0^x+q_0^y)}{v^x+v^y} - p^x(s) \nonumber \\
%   &= \frac{q_0^xv^y-q_0^yv^x+p^yv^x-p^xv^y}{v^x+v^y} \nonumber \\
   &= \frac{q_0^xv^y-q_0^yv^x+p^y(s)v^x-p^x(s)v^y}{v^x+v^y} \nonumber \\
   &= \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y+s(u^yv^x-u^xv^y)}{v^x+v^y} \nonumber \\
   &= s\frac{u^yv^x-u^xv^y}{v^x+v^y}+\frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{v^x+v^y} \label{eqn:a}
\end{align}
